Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-18 analysis/paper/paper.Rmd
add different models for spd

# zoom in in on the 40-33ka period GP is trying
spd_test_zoom <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(40000,30000),model='exponential',nsim=200,ncores=3)
summary(spd_test_zoom)
plot(spd_test_zoom)
```

>>>>

# zoom in in on the 40-30ka period GP is trying
spd_test_zoom <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(40000,30000),model='exponential',nsim=200,ncores=3)
summary(spd_test_zoom)
plot(spd_test_zoom)

# zoom in in on the 40-30ka period, testing other models
uni_test <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(40000,30000), model='uniform',nsim=200,ncores=3)
plot(uni_test)

lin_test <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(40000,30000), model='linear',nsim=200,ncores=3)
plot(lin_test)
```
